---
title: "RwithR"
author: "Rama Yedla"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# A Comprehensive guide towards learning R

This document helps the practitioners as a guide to quikly search for a section. The sections can help in finding out the answers that you are looking for.

Parallely, for first time learners, this document serves as a source to go through different ways R can be used and the problems it can solve.

## 1. Explore R Datasets

You can see the list of datasets available after you type datasets::. You can assign the preferred dataset to a variable and start exploring

```{r datasets}
airmiles <- datasets::airmiles
```

Datasets are stored in an R package. You can get the information about all the datasets available by doing the below

```{r datasets help}
library(help = 'datasets')
```

## 2. Vector Math

R is a nice calculator, I use R extensively for my personal finance (which I suck at) and it is very helpful.

Let's dive in and see what R can do...

```{r math}
8 + 4 #Addition
8 - 4 #Subtraction
8 * 4 #Multiplication
8 / 4 #Division
8 ** 4 #Exponentiation
```

## 3. Subsetting

Often, you will have to work with the subsets of the data to answer questions. We will learn about subsetting and en route, go through a few examples.

```{r}
#Let's take a vector and try different ways of subsetting it

numbers1 <- c(1:10)

#subset an item by the position
numbers1[2]

#Subset multiple sequence items based on position
numbers1[1:3]

#Subset multiple non sequence items based on position
numbers1[c(1, 3, 6, 9)]

#Subset items excluding a few
numbers1[-3]
numbers1[-3:-5]
numbers1[-c(3:5)] #This is same as the above
numbers1[-c(3, 7)]

#Subsetting by using a logical vector
logi <- rep(c(TRUE, FALSE), 5)
numbers1[logi]

#Let's dive into the subsetting of dataframes
#Create a dataframe
data <- data.frame(Name = LETTERS, Score = round(rnorm(26, mean = 78, sd = 10),0), Id = 1:26) 
head(data)

#start subsetting
data[3,] #entire 3rd row
data[,3] #entire 3rd column by position
data['Name'] #entire 1st column by column name
data[3:7, 2:3] #Choice of rows and columns

data[data$Score > 80,] #Subsetting rows with score > 80
data[data$Score > 80 & data$Id < 20,] #Subsetting rows with score > 80 and Id < 20
```

