---
title: "RwithR"
author: "Rama Yedla"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# A Comprehensive guide towards learning R

This document helps the practitioners as a guide to quikly search for a section. The sections can help in finding out the answers that you are looking for.

Parallely, for first time learners, this document serves as a source to go through different ways R can be used and the problems it can solve.

## 1. Explore R Datasets

You can see the list of datasets available after you type datasets::. You can assign the preferred dataset to a variable and start exploring

```{r datasets}
airmiles <- datasets::airmiles
```

Datasets are stored in an R package. You can get the information about all the datasets available by doing the below

```{r datasets help}
library(help = 'datasets')
```

## 2. Vector Math

R is a nice calculator, I use R extensively for my personal finance (which I suck at) and it is very helpful.

Let's dive in and see what R can do...

```{r pressure}
#Addition
5 + 3

#SUbtraction
5-3

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
